### 2014-02-27 paper/concrete.tex
Updated concrete.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

%{
%format tyerase c = "\varepsilon("c")"
%format tyerasef = "\varepsilon"
%format ^ = " "
%format c = "c"
%format c'
%format cc = "\con{"c"}"
%format cc'
%format ac = "\abs{"c"}"
%format ac'
%format V = "V"
%format cV = "\con{"V"}"
%format aV = "\abs{"V"}"
%format ~= = "\approx_l"
%format clequiv = "\con{"~="}"
%format alequiv = "\abs{"~="}"
%format creduce = "\con{".->"}"
%format areduce = "\abs{".->"}"
%format creducestar = "\con{".=>"}"
%format areducestar = "\abs{".=>"}"
%format (ap (f) (x)) = f"("x")"

@@

\begin{definition}[Inclusion of information-flow control languages]
    A language \con{|(C, Ce, V, .->, erasef l)|} is included in another
    language \abs{|(C, Ce, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
    |f| is a bijection over |l|-equivalences (|cc clequiv cc'| if and only if
    |(ap f cc) alequiv (ap f cc')|),
    preserves values (if |subseteq cc cV| then |subseteq (ap f cc) aV|) and is
    functorial over |.=>| (if
    |cc creducestar cc'| then |(ap f cc) areducestar (ap f cc')|).
\end{definition}

@@

\begin{definition}[Isomorphism of information-flow control languages]
    A language $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ is
    isomorphic to \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist total functions
    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and $f$ and $f^{-1}$ are
    functorial over both $l$-equivalences (if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
\end{definition}

>>>>

%{
%format tyerase c = "\varepsilon("c")"
%format tyerasef = "\varepsilon"
%format ^ = " "
%format c = "c"
%format c'
%format cc = "\con{"c"}"
%format cc'
%format ac = "\abs{"c"}"
%format ac'
%format finv = f"^{-1}"
%format V = "V"
%format cV = "\con{"V"}"
%format aV = "\abs{"V"}"
%format ~= = "\approx_l"
%format clequiv = "\con{"~="}"
%format alequiv = "\abs{"~="}"
%format creduce = "\con{".->"}"
%format areduce = "\abs{".->"}"
%format creducestar = "\con{".=>"}"
%format areducestar = "\abs{".=>"}"
%format (ap (f) (x)) = f"("x")"
%format .. = "\circ"
%format idf (t) = "id_{"t"}"

@@

\begin{definition}[Inclusion of information-flow control languages]
    A language \con{|(C, V, .->, erasef l)|} is included in another
    language \abs{|(C, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
    |f| is a bijection over |l|-equivalences (|cc clequiv cc'| if and only if
    |(ap f cc) alequiv (ap f cc')|),
    preserves values (if |subseteq cc cV| then |subseteq (ap f cc) aV|) and is
    functorial over |.=>| (if
    |cc creducestar cc'| then |(ap f cc) areducestar (ap f cc')|).
\end{definition}

@@

\begin{definition}[Isomorphism of information-flow control languages]
    A language \con{|(C, .->, erasef l)|} is
    isomorphic to a language \abs{|iC, .->, erasef l|} are isomorphic if there exist total functions
    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|, |finv .. f = idf iC|, and |f| and |finv| are
    functorial over both $l$-equivalences (if |cc clequiv
    cc'| then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
\end{definition}
